Age-related changes in plant growth and traits

### 2016-02-25 Accessory_figs_20160218.Rmd
accessory cost ms

#Figure 1. Correlations of various reproductive investment categories against plant weight
```{r}
win.metafile("figs2/Accessory_Costs/Figure01_correlations_with_plant_weight.wmf", height=9, width=13)
plot

par(mfrow=c(2,2), cex=1, omi=c(.1,0.1,.1,0.05), mai=c(.7,.55,.1,0.1))
options(scipen = 2)

@@

fit <- sma(data[[yvar]] ~ data[[xvar]]*data[["species"]], method="OLS", log="xy")
results <- lines(fit$groupsummary)
plot(fit,col=col.spp(fit$groupsummary$group),log="xy",ylim=c(1,300000),xlim=c(10,10000000),xlab="",ylab="",lty=results$linetype,pch=20)
mod <- lm(log10(total_weight_0)~log10(repro_inv),data=subset(SummaryInd,repro_inv>0))
words.top.left.logxy(mod)
mtext(text="total reproductive investment (mg)",side=2,line=2.3,outer=FALSE)
mtext(text="total plant weight (mg)",side=1,line=2,outer=FALSE)
Table_best_corr <- as.data.frame("total plant weight")
Table_best_corr <- bind_cols(Table_best_corr,select(glance(mod),r.squared,p.value),as.data.frame(mod$coefficients[1]),as.data.frame(mod$coefficients[2]))
names(Table_best_corr) <- c("investment category (mg)","r squared","p value","intercept","slope")

@@

fit <- sma(data[[yvar]] ~ data[[xvar]]*data[["species"]], method="OLS", log="xy")
results <- lines(fit$groupsummary)
plot(fit,col=col.spp(fit$groupsummary$group),log="xy",ylim=c(1,300000),xlab="",ylab="",lty=results$linetype,pch=20)
mod <- lm(log10(propagule_inv)~log10(repro_inv),data=subset(SummaryInd,propagule_inv>0))
words.top.left.logxy(mod)
mtext(text="investment in propagules (mg)",side=1,line=2,outer=FALSE)
new_row <- as.data.frame("propagules")
new_row <- bind_cols(new_row,select(glance(mod),r.squared,p.value),as.data.frame(mod$coefficients[1]),as.data.frame(mod$coefficients[2]))
names(new_row) <- c("investment category (mg)","r squared","p value","intercept","slope")
Table_best_corr <- bind_rows(Table_best_corr,new_row)

@@

fit <- sma(data[[yvar]] ~ data[[xvar]]*data[["species"]], method="OLS", log="xy",slope.test=1)
results <- lines(fit$groupsummary)
plot(fit,xlab="",ylab="",pch=16, col=col.spp(fit$groupsummary$group),lty=results$linetype,ylim=c(1,300000))
mtext(text="buds initiated",side=1,line=2,outer=FALSE)

@@

fit <- sma(data[[yvar]] ~ data[[xvar]]*data[["species"]], method="OLS", log="xy",slope.test=1)
results <- lines(fit$groupsummary)
plot(fit,xlab="",ylab="",pch=16, col=col.spp(fit$groupsummary$group),lty=results$linetype,ylim=c(1,300000))
mtext(text="flower weight * bud count",side=2,line=2,outer=FALSE)
mod <- lm(log10(flower_inv)~log10(repro_inv),data=subset(SummaryInd,flower_inv>0))
new_row <- as.data.frame("flower weight * bud count")
new_row <- bind_cols(new_row,select(glance(mod),r.squared,p.value),as.data.frame(mod$coefficients[1]),as.data.frame(mod$coefficients[2]))
names(new_row) <- c("investment category (mg)","r squared","p value","intercept","slope")
Table_best_corr <- bind_rows(Table_best_corr,new_row)

@@

@@

#Figure 2 and Table 3. Scaling of accessory costs versus seed size, by species
```{r}
win.metafile("figs2/Accessory_Costs/Figure02_acc_cost_seed_size.wmf", height=4, width=4)
plot

par(mfrow=c(1,1), cex=1, omi=c(.1,.1,.1,.1), mai=c(.8,.8,.3,.1)) 
options(scipen = 5)

plot(accessory_per_seed ~ seed_size,data=subset(SummarySpp[["mean"]]),col=col.spp(species),pch=16,log="xy", ylim=c(.02,10000), ylab="total per seed accessory costs (mg/seed)",xlab="seed size (mg)",cex=1.5)
mod <- lm(log10(accessory_per_seed) ~ log10(seed_size),data=subset(SummarySpp[["mean"]],accessory_per_seed>0))
y.error.bars(SummarySpp[["mean"]]$seed_size,SummarySpp[["mean"]]$accessory_per_seed,SummarySpp[["se"]]$accessory_per_seed)
slopes <- sma(log10(accessory_per_seed) ~ log10(seed_size),data=subset(SummarySpp[["mean"]]),slope.test=1)
abline(slopes$groupsummary["Int"][[1]],slopes$groupsummary["Slope"][[1]])
abline(slopes$groupsummary["Int"][[1]],1,col="red")
acc_by_species <- select(slopes$groupsummary,r2,pval,Slope,Slope_lowCI,Slope_highCI,Int,Int_lowCI,Int_highCI,Slope_test_p)
dev.off()

@@

#species with bigger seeds, lower seedset spend less per flower. Here taking the percent of the cost to make a single flower that goes into pre-pollination parts
```{r}
win.metafile("figs2/Accessory_Costs/Figure_costs_to_make_1_seed.wmf", height=4, width=12)
plot

par(mfrow=c(1,3), cex=1, omi=c(.8,0.1,.1,0.05), mai=c(.1,.8,.1,0.1))

yvar <- "seedcosts"
xvar <- "seed_size"
data <- subset(SummarySpp[["mean"]])
plot(seedcosts~seed_size,data=data,col=col.spp(species),pch=16,log="xy",cex=1.5,xlab="",ylab="all costs to make 1 seed (mg) = seedcosts")
slopes <- sma(data[[yvar]] ~ data[[xvar]], method="OLS", slope.test=1,log="xy")
abline(slopes$groupsummary["Int"][[1]],slopes$groupsummary["Slope"][[1]])
abline(slopes$groupsummary["Int"][[1]],1,col="red")
extra.topleft.logxy("total accessory costs required to produce 1 seed are lower for smaller seeded species")
seedcosts_by_species <- select(slopes$groupsummary,r2,pval,Slope,Slope_lowCI,Slope_highCI,Int,Int_lowCI,Int_highCI,Slope_test_p)

yvar <- "percent_prepollencosts"
plot(percent_prepollencosts~seed_size,data=subset(SummarySpp[["mean"]]),col=col.spp(species),pch=16,log="xy",cex=1.5,xlab="",ylab="prop seedcosts for prepollination")
extra.topleft.logxy("species with big seeds have low costs of producing a single flower")
slopes <- sma(data[[yvar]] ~ data[[xvar]], method="OLS", slope.test=1,log="xy")
abline(slopes$groupsummary["Int"][[1]],slopes$groupsummary["Slope"][[1]])
# abline(slopes$groupsummary["Int"][[1]],-1,col="red")
seedcosts_by_species <- dplyr::bind_rows(seedcosts_by_species, select(slopes$groupsummary,r2,pval,Slope,Slope_lowCI,Slope_highCI,Int,Int_lowCI,Int_highCI,Slope_test_p))

@@

seedcosts_by_species$variable = c("total seedcosts","prepollen costs (% of total)","dispersal costs (% of total)")
write.csv(seedcosts_by_species, file="figs2/Accessory_Costs/Table04_seedcosts_by_species.csv",row.names=FALSE)
dev.off()
```

@@

@@

par(mfrow=c(1,1), cex=1, omi=c(.4,.4,.1,.1), mai=c(.8,.8,.2,.2)) 
plot(ovules_per_fruit~slope,data=subset(results),log="y",col=col.spp(species),pch=16,cex=2,ylab="ovules per fruit",xlab="slope between dispersal costs and seedset")

mod <- lm(slope~log10(ovules_per_fruit),data=subset(results))
words.top.right.logy(mod)
dev.off()

@@

#Higher RE, RA, plant size do not lead to lower accessory costs; age shows mixed results
##Not a single species shows a reduction in per seed accessory costs with increased plant size.Indeed, EPMI has higher pre-pollination accessory costs    (slope = 0.38, r2=0.19, p=0.019) and accessory costs due to aborted fruit and seeds (slope = 0.83, r2=0.268, p=0.019) in larger individuals, as larger individuals of this species have lower seedset (slope = -0.31, r2=0.198, p=0.018). GRSP also has a nearly significant decline in seedset in larger individuals (slope = -0.78, r2=0.298, p=0.067).
```{r}
win.metafile("figs2/Accessory_Costs/Figure_RE_RA_size_age_patterns.wmf", height=8, width=8)
plot

par(mfrow=c(2,2), cex=1, omi=c(.1,0.4,.1,0.05), mai=c(.6,.3,.1,0.1))
options(scipen = 2)

@@

#Considering the individual components of accessory costs vs. seedset - since seedset best predictor of accessory costs

#For each species the accessory cost components that cause shifts in total accessory costs is different and reflects both which components are largest and whichvary most with some factor - seedset, age, etc.
```{r}
xvar1 <- "packaging_dispersal_per_seed"
xvar2 <- "b_div_p"
xvar3 <- "c_div_p"
yvar <- "accessory_per_seed"
data <- subset(SummaryInd,SummaryInd[[xvar1]]>0&SummaryInd[[xvar2]]>0&SummaryInd[[xvar3]]>0)
data <- split(data, data$species)

@@

for(i in 1:13) {
     species_coef <- dplyr::bind_cols(species_coef, as.data.frame(mod[[i]]$coefficients))
     }

names(species_coef) <- c("effect","BAER","BOLE","COER","EPMI","GRBU","GRSP","HATE","HEPU","PELA","PEPU","PHPH","PILI","PUTU")

LEES_c <- as.data.frame(mod_LEES$coefficients)
LEES_c$effect <- c("intercept","b_div_p","c_div_p")
names(LEES_c) <- c("LEES","effect")

species_coef <- dplyr::left_join(species_coef,LEES_c,by="effect")

species_t <- as.data.frame(c("intercept","packaging&dispersal","b_div_p","c_div_p"))
#species_t <- dplyr::bind_cols(species_t, as.data.frame(summary(mod_BAER$coefficient)[,4])))
species_t <- dplyr::bind_cols(species_t, as.data.frame(summary(mod[[2]])$coefficient[,4]))
species_t <- dplyr::bind_cols(species_t, as.data.frame(summary(mod[[4]])$coefficient[,4]))
species_t <- dplyr::bind_cols(species_t, as.data.frame(summary(mod[[5]])$coefficient[,4]))
species_t <- dplyr::bind_cols(species_t, as.data.frame(summary(mod[[6]])$coefficient[,4]))
species_t <- dplyr::bind_cols(species_t, as.data.frame(summary(mod[[7]])$coefficient[,4]))
species_t <- dplyr::bind_cols(species_t, as.data.frame(summary(mod[[8]])$coefficient[,4]))
species_t <- dplyr::bind_cols(species_t, as.data.frame(summary(mod[[9]])$coefficient[,4]))
species_t <- dplyr::bind_cols(species_t, as.data.frame(summary(mod[[10]])$coefficient[,4]))
species_t <- dplyr::bind_cols(species_t, as.data.frame(summary(mod[[11]])$coefficient[,4]))
species_t <- dplyr::bind_cols(species_t, as.data.frame(summary(mod[[12]])$coefficient[,4]))
species_t <- dplyr::bind_cols(species_t, as.data.frame(summary(mod[[13]])$coefficient[,4]))
names(species_t) <- c("effect","BOLE","EPMI","GRBU","GRSP","HATE","HEPU","PELA","PEPU","PHPH","PILI","PUTU")

xvar1 <- "packaging_dispersal_per_seed"
xvar2 <- "b_div_p"
xvar3 <- "c_div_p"
yvar <- "accessory_per_seed"
data <- subset(SummaryInd,SummaryInd[[xvar2]]>0&SummaryInd[[xvar3]]>0&species=="LEES")

summary(mod)

write.csv(species_coef, file="figs2/Accessory_Costs/Table08_breaking_down_accessory_costs_spp.csv",row.names=FALSE)
```

@@

plot(per_seed~seedcosts,ternary,col="black",log="x",pch=21,cex=2,ylim=c(0,75),ylab="percent of seedcosts")
points(per_poll~seedcosts,ternary,col="red",pch=20,cex=2)
points(per_disp~seedcosts,ternary,col="blue",pch=20,cex=2)

@@

```{r}
win.metafile("figs2/Accessory_Costs/Ternary.wmf", height=6, width=6)
plot

ggtern(data=ternary,aes(y=per_seed,x=per_poll,z=per_disp)) +
  labs(y = "seed weight (%)",x = "prepoll (%)",z = "pack&disp (%)",title = "Seed cost components",size = 1) +
  geom_point(size=sqrt(ternary$seedcosts/2),shape=20,color=col.spp()) +
   theme_bw() + 
  geom_text(label=ternary$species, color="black", hjust=-.3, vjust=sqrt(ternary$seedcosts/500),size=2)

@@

?geom_text

>>>>

dev.off()
#Figure 1. Correlations of various reproductive investment categories against plant weight
```{r}
win.metafile("figs2/Accessory_Costs/Figure01_correlations_with_plant_weight.wmf", height=10, width=10)
plot

par(mfrow=c(2,2), cex=1, omi=c(.1,.6,.1,.05), mai=c(.8,.1,.1,.05))
options(scipen = 4)

@@

fit <- sma(data[[yvar]] ~ data[[xvar]]*data[["species"]], method="OLS", log="xy")
results <- lines(fit$groupsummary)
plot(fit,col=col.spp(fit$groupsummary$group),log="xy",ylim=c(1,300000),xlim=c(1,10000000),xlab="",ylab="",lty=results$linetype,pch=16)
mod <- lm(log10(total_weight_0)~log10(repro_inv),data=subset(SummaryInd,repro_inv>0))
abline(0,1)
words.top.left.logxy(mod)
mtext(text="total reproductive investment (mg)",side=2,line=2,outer=TRUE)
mtext(text="total plant weight (mg)",side=1,line=2,outer=FALSE)
Table_best_corr <- as.data.frame("total plant weight")
Table_best_corr <- bind_cols(Table_best_corr,select(glance(mod),r.squared,p.value),as.data.frame(mod$coefficients[1]),as.data.frame(mod$coefficients[2]))
names(Table_best_corr) <- c("investment category (mg)","r squared","p value","intercept","slope")

@@

fit <- sma(data[[yvar]] ~ data[[xvar]]*data[["species"]], method="OLS", log="xy")
results <- lines(fit$groupsummary)
plot(fit,col=col.spp(fit$groupsummary$group),log="xy",ylim=c(1,300000),xlim=c(1,300000), xlab="",ylab="",lty=results$linetype,pch=16)
abline(0,1)
mod <- lm(log10(propagule_inv)~log10(repro_inv),data=subset(SummaryInd,propagule_inv>0))
words.top.left.logxy(mod)
mtext(text="investment in propagules (mg)",side=1,line=2,outer=FALSE)
new_row <- as.data.frame("propagules")
new_row <- bind_cols(new_row,select(glance(mod),r.squared,p.value),as.data.frame(mod$coefficients[1]),as.data.frame(mod$coefficients[2]))
names(new_row) <- c("investment category (mg)","r squared","p value","intercept","slope")
Table_best_corr <- bind_rows(Table_best_corr,new_row)

@@

fit <- sma(data[[yvar]] ~ data[[xvar]]*data[["species"]], method="OLS", log="xy",slope.test=1)
results <- lines(fit$groupsummary)
plot(fit,xlab="",ylab="",pch=16, col=col.spp(fit$groupsummary$group),lty=results$linetype,ylim=c(1,300000),xlim=c(1,30000))
mtext(text="buds initiated",side=1,line=2,outer=FALSE)

@@

fit <- sma(data[[yvar]] ~ data[[xvar]]*data[["species"]], method="OLS", log="xy",slope.test=1)
results <- lines(fit$groupsummary)
plot(fit,xlab="",ylab="",pch=16, col=col.spp(fit$groupsummary$group),lty=results$linetype,ylim=c(1,300000),xlim=c(1,300000))
abline(0,1)
mtext(text="flower weight * bud count",side=1,line=2,outer=FALSE)
mod <- lm(log10(flower_inv)~log10(repro_inv),data=subset(SummaryInd,flower_inv>0))
new_row <- as.data.frame("flower weight * bud count")
new_row <- bind_cols(new_row,select(glance(mod),r.squared,p.value),as.data.frame(mod$coefficients[1]),as.data.frame(mod$coefficients[2]))
names(new_row) <- c("investment category (mg)","r squared","p value","intercept","slope")
Table_best_corr <- bind_rows(Table_best_corr,new_row)

@@

```{r}
win.metafile("figs2/Accessory_Costs/Figure02_seedsize_vs_reproinv.wmf", height=5, width=10)
plot

par(mfrow=c(1,2), cex=1, omi=c(.1,.1,.1,.05), mai=c(.8,.8,.1,.1))

plot(repro_inv~seed_size,SummarySpp[["mean"]],log="xy",col=col.spp(species),pch=16)
mod <- lm(log10(repro_inv)~log10(seed_size),SummarySpp[["mean"]])
abline(mod$coeff[1],mod$coeff[2])
words.top.left.logxy(mod)
y.error.bars(SummarySpp[["mean"]]$seed_size,SummarySpp[["mean"]]$repro_inv,SummarySpp[["se"]]$repro_inv)

plot(seedset~seed_size,SummarySpp[["mean"]],log="xy",col=col.spp(species),pch=16)
mod <- lm(log10(seedset)~log10(seed_size),SummarySpp[["mean"]])
abline(mod$coeff[1],mod$coeff[2])
words.bottom.left.logxy(mod)
y.error.bars(SummarySpp[["mean"]]$seed_size,SummarySpp[["mean"]]$seedset,SummarySpp[["se"]]$seedset)

@@

#Figure 2 and Table 3. Scaling of accessory costs versus seed size, by species
```{r}
win.metafile("figs2/Accessory_Costs/Figure02_seed_size_correlations.wmf", height=5, width=20)
plot

par(mfrow=c(1,4), cex=1, omi=c(.6,.1,.05,.05), mai=c(.1,.8,.05,.05)) 
options(scipen = 5)

yvar <- "seedcosts"
xvar <- "seed_size"
data <- subset(SummarySpp[["mean"]])
plot(seedcosts~seed_size,data=data,col=col.spp(species),pch=16,log="xy",cex=1.5,xlab="",ylab="all costs to make 1 seed (mg) = seedcosts",ylim=c(.02,20000), xlim=c(.02,20000))
slopes <- sma(data[[yvar]] ~ data[[xvar]], method="OLS", slope.test=1,log="xy")
mod <- lm(log10(seedcosts)~log10(seed_size),SummarySpp[["mean"]])
abline(slopes$groupsummary["Int"][[1]],slopes$groupsummary["Slope"][[1]])
#abline(slopes$groupsummary["Int"][[1]],1,col="red")
abline(0,1,col="red")
words.top.left.logxy(mod)

plot(accessory_per_seed ~ seed_size,data=subset(SummarySpp[["mean"]]),col=col.spp(species),pch=16,log="xy", ylim=c(.02,20000), xlim=c(.02,20000), ylab="total per seed accessory costs (mg/seed)",xlab="",cex=1.5)
mod <- lm(log10(accessory_per_seed) ~ log10(seed_size),data=subset(SummarySpp[["mean"]],accessory_per_seed>0))
y.error.bars(SummarySpp[["mean"]]$seed_size,SummarySpp[["mean"]]$accessory_per_seed,SummarySpp[["se"]]$accessory_per_seed)
slopes <- sma(log10(accessory_per_seed) ~ log10(seed_size),data=subset(SummarySpp[["mean"]]),slope.test=1)
abline(slopes$groupsummary["Int"][[1]],slopes$groupsummary["Slope"][[1]])
#abline(slopes$groupsummary["Int"][[1]],1,col="red")
abline(0,1,col="red")
words.bottom.left.logxy(mod)

plot(repro_inv~seed_size,SummarySpp[["mean"]],log="xy",ylab="reproductive investment (mg)",col=col.spp(species),pch=16, ylim=c(.02,20000), xlim=c(.02,20000),cex=1.5)
mod <- lm(log10(repro_inv)~log10(seed_size),data=subset(SummarySpp[["mean"]],species!="EPMI"))
abline(mod$coeff[1],mod$coeff[2])
words.bottom.left.logxy(mod)
y.error.bars(SummarySpp[["mean"]]$seed_size,SummarySpp[["mean"]]$repro_inv,SummarySpp[["se"]]$repro_inv)
abline(0,1,col="red")

plot(seedset~seed_size,SummarySpp[["mean"]],log="xy",col=col.spp(species),pch=16, xlim=c(.02,20000),cex=1.5)
mod <- lm(log10(seedset)~log10(seed_size),SummarySpp[["mean"]])
abline(mod$coeff[1],mod$coeff[2])
words.bottom.left.logxy(mod)
y.error.bars(SummarySpp[["mean"]]$seed_size,SummarySpp[["mean"]]$seedset,SummarySpp[["se"]]$seedset)

mtext(text="seed size (mg)",side=1,line=2,outer=TRUE)

```{r}
plot(accessory_per_seed ~ seed_size,data=subset(SummarySpp[["mean"]]),col=col.spp(species),pch=16,log="xy", ylim=c(.02,10000), xlim=c(.02,10000), ylab="total per seed accessory costs (mg/seed)",xlab="",cex=1.5)
mod <- lm(log10(accessory_per_seed) ~ log10(seed_size),data=subset(SummarySpp[["mean"]],accessory_per_seed>0))
y.error.bars(SummarySpp[["mean"]]$seed_size,SummarySpp[["mean"]]$accessory_per_seed,SummarySpp[["se"]]$accessory_per_seed)
slopes <- sma(log10(accessory_per_seed) ~ log10(seed_size),data=subset(SummarySpp[["mean"]]),slope.test=1)
abline(slopes$groupsummary["Int"][[1]],slopes$groupsummary["Slope"][[1]])
#abline(slopes$groupsummary["Int"][[1]],1,col="red")
abline(0,1,col="red")
words.bottom.right.logxy(mod)

acc_by_species <- select(slopes$groupsummary,r2,pval,Slope,Slope_lowCI,Slope_highCI,Int,Int_lowCI,Int_highCI,Slope_test_p)

@@

#species with bigger seeds, lower seedset spend less per flower. Here taking the percent of the cost to make a single flower that goes into pre-pollination parts
```{r}
win.metafile("figs2/Accessory_Costs/Figure_seedcosts_vs_seedsize.wmf", height=5, width=5)
plot

par(mfrow=c(1,1), cex=1, omi=c(.1,.1,.1,.05), mai=c(.8,.8,.1,.1))

yvar <- "seedcosts"
xvar <- "seed_size"
data <- subset(SummarySpp[["mean"]])
plot(seedcosts~seed_size,data=data,col=col.spp(species),pch=16,log="xy",cex=1.5,xlab="seed size (mg)",ylab="all costs to make 1 seed (mg) = seedcosts",ylim=c(.02,10000), xlim=c(.02,10000))
slopes <- sma(data[[yvar]] ~ data[[xvar]], method="OLS", slope.test=1,log="xy")
mod <- lm(log10(seedcosts)~log10(seed_size),SummarySpp[["mean"]])
abline(slopes$groupsummary["Int"][[1]],slopes$groupsummary["Slope"][[1]])
#abline(slopes$groupsummary["Int"][[1]],1,col="red")
abline(0,1,col="red")
extra.topleft.logxy("total accessory costs required to produce 1 seed are lower for smaller seeded species")
words.bottom.right.logxy(mod)
seedcosts_by_species <- select(slopes$groupsummary,r2,pval,Slope,Slope_lowCI,Slope_highCI,Int,Int_lowCI,Int_highCI,Slope_test_p)
dev.off()
```

```{r}
xvar <- "seed_size"
yvar <- "percent_prepollencosts"
data <- subset(SummarySpp[["mean"]])
plot(percent_prepollencosts~seed_size,data=subset(SummarySpp[["mean"]]),col=col.spp(species),pch=16,log="xy",cex=1.5,xlab="",ylab="prop seedcosts for prepollination")
extra.topleft.logxy("species with big seeds have low costs of producing a single flower")
slopes <- sma(data[[yvar]] ~ data[[xvar]], method="OLS", slope.test=1,log="xy")
abline(slopes$groupsummary["Int"][[1]],slopes$groupsummary["Slope"][[1]])
# abline(slopes$groupsummary["Int"][[1]],-1,col="red")
seedcosts_by_species <- dplyr::bind_rows(seedcosts_by_species, select(slopes$groupsummary,r2,pval,Slope,Slope_lowCI,Slope_highCI,Int,Int_lowCI,Int_highCI,Slope_test_p))

@@

seedcosts_by_species$variable = c("total seedcosts","prepollen costs (% of total)","dispersal costs (% of total)")
write.csv(seedcosts_by_species, file="figs2/Accessory_Costs/Table04_seedcosts_by_species.csv",row.names=FALSE)
```

@@

```{r}
win.metafile("figs2/Accessory_Costs/Figure_acc_cost_by_seedset.wmf", height=5, width=5)
plot

par(mfrow=c(1,1), cex=1, omi=c(.5,.1,.1,.1), mai=c(.1,1,.3,.1))

xvar <- "seed_size"
yvar <- "seedcosts"

plot(seedcosts~seed_size,data=subset(SummaryInd,SummaryInd[[xvar]]>0&SummaryInd[[yvar]]>0),log="xy",pch=16,col=col.spp(species),cex=2)
mod <-lm(log10(seedcosts)~log10(seed_size),SummaryInd)
abline(mod$coeff[1],mod$coeff[2])
words.top.left.logxy(mod)

#text((10^(par()$usr[1])*1.4),(10^(par()$usr[4])*.8),summary(mod)$coefficients[1,1])
dev.off()
```

@@

par(mfrow=c(1,1), cex=1, omi=c(.4,.4,.1,.1), mai=c(.8,.8,.2,.2)) 
plot(ovules_per_fruit~r2,data=subset(results),log="y",col=col.spp(species),pch=16,cex=2,ylab="ovules per fruit",xlab="slope between dispersal costs and seedset")
mod <- lm(log10(ovules_per_fruit)~r2,data=subset(results,species!="PELA"))
abline(mod$coeff[1],mod$coeff[2])
words.top.left.logy(mod)
dev.off()

@@

#Higher RE, RA, plant size do not lead to lower accessory costs; age shows mixed results
##Not a single species shows a reduction in per seed accessory costs with increased plant size.Indeed, EPMI has higher pre-pollination accessory costs    (slope = 0.38, r2=0.19, p=0.019) and accessory costs due to aborted fruit and seeds (slope = 0.83, r2=0.268, p=0.019) in larger individuals, as larger individuals of this species have lower seedset (slope = -0.31, r2=0.198, p=0.018). GRSP also has a nearly significant decline in seedset in larger individuals (slope = -0.78, r2=0.298, p=0.067).
```{r}
win.metafile("figs2/Accessory_Costs/Figure_RE_RA_size_age_patterns.wmf", height=10, width=10)
plot

par(mfrow=c(2,2), cex=1, omi=c(.1,.4,.1,.05), mai=c(.6,.3,.1,.1))
options(scipen = 2)

@@

```{r}
win.metafile("figs2/Accessory_Costs/Figure_seedcount_reprocount.wmf", height=5, width=5)
plot

par(mfrow=c(1,1), cex=1, omi=c(.1,0.1.1,0.05), mai=c(.8,.8,.1,0.1))
options(scipen = 2)

xvar <- "prepollen_all_count"
yvar <- "seed_count"
data <- subset(SummaryInd,SummaryInd[[xvar]]>0&SummaryInd[[yvar]]>0)

fit <- sma(data[[yvar]] ~ data[[xvar]]*data[["species"]], method="OLS", log="xy")
results <- lines(fit$groupsummary)
plot(fit,col=col.spp(fit$groupsummary$group),pch=16,xlab="buds initiated (count)",ylab="seed count",lty=results$linetype,xlim=c(0.9,20000),ylim=c(0.9,20000))

abline(0,1,lwd=2)
abline(-2,1,lwd=2)

legend_with_r2(results,"topleft")

summary(results)
summary(fit)

fit2 <- sma(data[[yvar]] ~ data[[xvar]]*data[["species"]], log="xy",slope.text=1)
summary(fit2)

dev.off()
```
#Considering the individual components of accessory costs vs. seedset - since seedset best predictor of accessory costs

#For each species the accessory cost components that cause shifts in total accessory costs is different and reflects both which components are largest and whichvary most with some factor - seedset, age, etc.
```{r}
xvar1 <- "packaging_dispersal_per_seed"
xvar2 <- "b_div_p"
xvar3 <- "c_div_p"
yvar <- "accessory_per_seed"
data <- subset(SummaryInd,SummaryInd[[xvar1]]>0&SummaryInd[[xvar2]]>0&SummaryInd[[xvar3]]>0&species!="BAER"&species!="COER"&species!="LEES")
data <- split(data, data$species)

@@

for(i in 1:11) {
     species_coef <- dplyr::bind_cols(species_coef, as.data.frame(mod[[i]]$coefficients))
     }

names(species_coef) <- c("effect","BOLE","EPMI","GRBU","GRSP","HATE","HEPU","PELA","PEPU","PHPH","PILI","PUTU")

BAER_c <- as.data.frame(mod_BAER$coefficients)
BAER_c$effect <- c("intercept","b_div_p","packaging&dispersal")
names(BAER_c) <- c("BAER","effect")
species_coef <- dplyr::left_join(species_coef,BAER_c,by="effect")

COER_c <- as.data.frame(mod_COER$coefficients)
COER_c$effect <- c("intercept","b_div_p","packaging&dispersal")
names(COER_c) <- c("COER","effect")
species_coef <- dplyr::left_join(species_coef,COER_c,by="effect")

LEES_c <- as.data.frame(mod_LEES$coefficients)
LEES_c$effect <- c("intercept","b_div_p","c_div_p")
names(LEES_c) <- c("LEES","effect")
species_coef <- dplyr::left_join(species_coef,LEES_c,by="effect")

# Reorder by column name
species_coef <- species_coef[c("effect", "BAER", "BOLE", "COER", "EPMI", "GRBU", "GRSP", "HATE", "HEPU", "LEES", "PELA", "PEPU", "PHPH", "PILI", "PUTU")]

write.csv(species_coef, file="figs2/Accessory_Costs/Table08_accessory_components_coeff.csv",row.names=FALSE)

species_t <- as.data.frame(c("intercept","packaging&dispersal","b_div_p","c_div_p"))

for(i in 1:11) {
     species_t <- dplyr::bind_cols(species_t, as.data.frame(summary(mod[[i]])$coefficient[,4]))
     }

names(species_t) <- c("effect","BOLE","EPMI","GRBU","GRSP","HATE","HEPU","PELA","PEPU","PHPH","PILI","PUTU")

BAER_t <- as.data.frame(summary(mod_BAER)$coefficient[,4])
BAER_t$effect <- c("intercept","b_div_p","packaging&dispersal")
names(BAER_t) <- c("BAER","effect")
species_t <- dplyr::left_join(species_t,BAER_t,by="effect")

COER_t <- as.data.frame(summary(mod_COER)$coefficient[,4])
COER_t$effect <- c("intercept","b_div_p","packaging&dispersal")
names(COER_t) <- c("COER","effect")
species_t <- dplyr::left_join(species_t,COER_t,by="effect")

LEES_t <- as.data.frame(summary(mod_LEES)$coefficient[,4])
LEES_t$effect <- c("intercept","b_div_p","c_div_p")
names(LEES_t) <- c("LEES","effect")
species_t <- dplyr::left_join(species_t,LEES_t,by="effect")

# Reorder by column name
species_t <- species_t[c("effect", "BAER", "BOLE", "COER", "EPMI", "GRBU", "GRSP", "HATE", "HEPU", "LEES", "PELA", "PEPU", "PHPH", "PILI", "PUTU")]

write.csv(species_t, file="figs2/Accessory_Costs/Table08_accessory_components_t-value.csv",row.names=FALSE)

```

@@

plot(per_seed~seedcosts,ternary,col="black",log="x",pch=21,cex=2,ylim=c(0,75),ylab="percent of seedcosts")
points(per_poll~seedcosts,ternary,col="red",pch=16,cex=2)
points(per_disp~seedcosts,ternary,col="blue",pch=16,cex=2)

@@

```{r}
win.metafile("figs2/Accessory_Costs/Ternary.wmf", height=5, width=5)
plot

ggtern(data=ternary,aes(y=per_seed,x=per_poll,z=per_disp)) +
  labs(y = "seed weight (%)",x = "prepoll (%)",z = "pack&disp (%)",title = "Seed cost components",size = .5) +
  geom_point(size=sqrt(ternary$seedcosts/2),shape=20,color=col.spp()) +
   theme_bw() + 
  geom_text(label=ternary$species, color="black", hjust=-.3, vjust=sqrt(ternary$seedcosts/500),size=2)

@@
